Automated Residual Plot Assessment with the R Package autovi and Shiny App autovi.web

### 2024-11-25 autovi_paper.qmd
fix metadata (including abstract)

subtitle: ANZJS Quarto Template

@@

      - template-header.tex

@@

  Regression software is widely available, and there are many tools for generating diagnostics and computing conventional residual tests. However, the advice remains that the analyst should look at the residual plot to check the fit. Perhaps, one of the reasons is that conventional tests are too sensitive, strictly resulting in adequate models being abandoned. Visually assess the strength of patterns in residual plots requires human effort and suffers from the potential for inconsistent decisions from different analysts. Using a lineup protocol, where the residual plot is embedded among null plots, can help to alleviate inconsistency, but requires even more human effort. This is the type of task that in today's world might employ a robot to do the tedious work for a human. Here we describe a new R package that includes a computer vision model for automated assessment of residual plots, and an accompanying Shiny app for ease of use. For a user-provided sample of residuals, it predicts a measure of visual signal strength (VSS) and provides a suite of supporting information to assist the analyst decide on the appropriateness their model fit. 

>>>>

@@

      - header.tex

@@

  Visually assessing residual plots is the common advice for linear model diagnostics, however this approach requires manual human evaluation and thereby is not a scalable approach. Human evaluation also suffer from the potential for inconsistent decisions from different analysts. Using a lineup protocol, where the residual plot is embedded among null plots, can help to alleviate inconsistency, but requires even more human effort. This is the type of task that in today's world might employ a robot to do the tedious work for a human. Here we describe a new R package that includes a computer vision model for automated assessment of residual plots, and an accompanying Shiny app for ease of use. For a user-provided sample of residuals, it predicts a measure of visual signal strength (VSS) and provides a suite of supporting information to assist the analyst decide on the appropriateness their model fit. 
